Verifying Demonstrations

### 2017-08-25 properties.tex
Replaces blockchain with t-poset
Adds t-poset figure to slides
Moves dependency tree figure

\begin{figure}
  \centering
  \begin{tikzpicture}[->,auto,node distance=1.5cm,thick,
    proof node/.style={rectangle,draw},
    time node/.style={circle,draw}]

@@

  \end{tikzpicture}
  \mode<article>{%
    \caption{%
      Alice submits proof \(p_A\) and Bob submits proof \(p_B\).
      We have \(t_s\prec p_A, p_B\prec t_e\), but \((p_A, p_B)\notin \prec\) 
      are incomparable.
    }\label{PosetGraph}
  }
\end{figure}

@@

We will introduce a notion of transitivity for trust in these proofs.
The \emph{trusted} journalist Jane the protest to report on it.
She witnesses some participants' \acp{LP}, say Alice's \ac{LP} for example.
Now Alice's \ac{LP} can be trusted as correct at that point in time.
Alice's ability to travel is physically limited.
Thus a verifier can trust any \ac{LP} that Alice witnesses proportionally to 
the time that has passed since Jane witnessed Alice's \ac{LP}.
We can apply this argument recursively for any other participant's \ac{LP} that 
Alice has witnessed.
However, this requires some assumptions:
\begin{itemize}
  \item It is actually Alice's signing key must have physically limited travel.
    This can be assumed for signing keys that are embedded into hardware by 
    some trusted person.
  \item Alice's witness signature must depend on Jane's witness signature, to 
    prove that Alice signed after Jane.
\end{itemize}
\begin{remark}
  This probably requires high-precision timestamps, i.e.\ a trusted 
  time-stamping server must be available during the protest.
  Or the proofs must be submitted to the blockchain during the protest.
\end{remark}

@@

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Count once]
    \begin{itemize}
      \item Any two proofs by the same individual are linkable.
      \item Includes signature made by a verified key.
    \end{itemize}
  \end{idea}

  \begin{idea}[Designated event]
    \begin{itemize}
      \item Include a protest-specific identifier.
      \item E.g.\ hash of the \enquote{manifesto}.
    \end{itemize}
  \end{idea}
\end{frame}
}

>>>>

\begin{frame}
\begin{figure}
  \centering
  \begin{tikzpicture}[->,auto,node distance=1.5cm,thick,
    proof node/.style={rectangle,draw},
    time node/.style={circle,draw}]

@@

  \end{tikzpicture}
  \mode<article>{%
    \caption{%
      Alice submits proof \(p_A\) and Bob submits proof \(p_B\).
      We have \(t_s\prec p_A, p_B\prec t_e\), but \((p_A, p_B)\notin \prec\) 
      are incomparable.
    }\label{PosetGraph}
  }
\end{figure}
\end{frame}

@@

We will introduce a notion of transitivity for trust in these proofs.
The \emph{trusted} journalist Jane the protest to report on it.
She witnesses some participants' \acp{LP}, say Alice's \ac{LP} for example.
Now Alice's \ac{LP} can be trusted as correct at that point in time.
Alice's ability to travel is physically limited.
Thus a verifier can trust any \ac{LP} that Alice witnesses proportionally to 
the time that has passed since Jane witnessed Alice's \ac{LP}.
We can apply this argument recursively for any other participant's \ac{LP} that 
Alice has witnessed.
However, this requires some assumptions:
\begin{itemize}
  \item It is actually Alice's signing key must have physically limited travel.
    This can be assumed for signing keys that are embedded into hardware by 
    some trusted person.
  \item Alice's witness signature must depend on Jane's witness signature, to 
    prove that Alice signed after Jane.
\end{itemize}
\begin{remark}
  This probably requires high-precision timestamps, i.e.\ a trusted 
  time-stamping server must be available during the protest.
  Or the proofs must be submitted to the \ac{tposet} during the protest.
\end{remark}

@@

\begin{frame}
\begin{figure}
  \centering
  \begin{tikzpicture}
    \tikzset{grow'=right,level distance=5em}
    \Tree [.Proof
      [.{wsig} {\(x,y\)} [.{\mode<presentation>{\only<1>{\color{red}}} osig} 
      [.{\mode<presentation>{\only<2>{\color{red}}}\(id\)} manifesto ] head ] 
      [.tsig head$'$ ] ]
      {\dots}
      [.{wsig} {\dots} ]
    ]
  \end{tikzpicture}
  \mode<article>{%
    \caption{%
      The proof depends on several witness signatures (wsig), each of which 
      depends on the owner's signature (osig), which depends on the \(id\) of the
      protest and the head of the \ac{tposet}.
      Whenever possible, the witness signature should include proof that the 
      witness themself has been witnessed by a trusted witness (tsig).
    }
  }
\end{figure}

\mode<presentation>{%
  \only<1>{%
    \begin{idea}[Count once]
      \begin{itemize}
        \item Any two proofs by the same individual are linkable.
        \item Includes signature made by a verified key.
      \end{itemize}
    \end{idea}
  }

  \only<2>{%
    \begin{idea}[Designated event]
      \begin{itemize}
        \item Include a protest-specific identifier.
        \item E.g.\ hash of the \enquote{manifesto}.
      \end{itemize}
    \end{idea}
  }
}
\end{frame}
